DisCon Kids Pilot

### 2019-03-02 analysis/02_kids_600.Rmd
update data file kids

---
title: "DisCon Kids Pilot"
output: html_document
---

@@

```{r data pre-processing}

@@

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

@@

data <- read_csv(file="../data/kids_600.data.csv")
```

@@

```{r}
data %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

@@

ggplot() +
  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .025)+
  geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1))

@@

# Model 
```{r}
library(brms)

@@

```{r}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)

>>>>

---
title: "DisCon Kids Pilot"
output: html_document
  code_folding: hide
---

@@

```{r data pre-processing, include = F}

@@

data <- left_join(raw_data,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(distribution = as.character(distribution),
         distribution = factor(distribution, levels = c("c(6, 0, 0)", "c(4, 2, 0)", "c(2, 2, 2)")),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  select(-dob, -check_age,-keep_drop,-experimenter,-test_date,-numberOfTrials,-nunberOfTrials)

@@

##data <- read_csv(file="../data/kids_600.data.csv")
```

@@

```{r}
data %>%
  group_by(subage
           #,sex
           )%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)
```

@@

ggplot() +
  geom_jitter(data = pt1, aes(x = subage, y = correct, col = subage, alpha = .2),width = .1,height = .0)+
  geom_pointrange(data = pt2, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 5/6, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

```{r proportion of choices}
p1 <- data %>%
  filter(phase == 'test')%>%
  group_by(experiment,subid) %>%
  summarise(correct = mean(correct_target1),
            sd = sd(correct_target1))

@@

# Model 
```{r, include = F}
library(brms)

@@

```{r, include = F}
kbm2 <- brm(correct_target1 ~ 1 +
                      (1| subid) + (1 | target1),
                    data = model_data, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 2000)
